Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-12 docs/ms.tex
Update ms.tex

However in our hierarchical Bayesian approach we are able to obtain
the posterior distribution of g, based on the assumption $\phi$ has
a uniform distribution and galaxies in different sky patches have
the same intrinsic shape distribution.

Suppose we know the ellipticity distribution of unlensed galaxies
based on some parasmeters $\alpha$, then we can write down the likelihood
of reduced shear and $\alpha$:

>>>>

However in our hierarchical Bayesian approach we are able to obtain
the posterior distribution of reduced shear, based on the assumption that $\phi$ has
a uniform distribution and galaxies in different sky patches have
the same intrinsic shape distribution.

Suppose we know the intrnsic ellipticity distribution P($\epslion_{0}$)
based on some parasmeters $\alpha$. Then we can write down the likelihood
of reduced shear and $\alpha$:
